%Two resources useful for abstract writing.
% Guidance of how to write an abstract/summary provided by Nature: https://cbs.umn.edu/sites/cbs.umn.edu/files/public/downloads/Annotated_Nature_abstract.pdf %https://writingcenter.gmu.edu/guides/writing-an-abstract
\chapter*{\center \Large  Abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Replace all text with your text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This is the official report template for the Shopis project, providing guidance on how to structure the documentation. It also includes practical examples demonstrating the use of \LaTeX. Please review this template thoroughly. The number of chapters and their titles may vary depending on the scope of the Shopis system and individual documentation preferences. Section titles in this template are illustrative and should be adapted accordingly. For instance, sections such as “A section...” and “Example of ...” must be renamed. The number of subsections per chapter may also vary.

%%%
~\\[1cm]%REMOVE THIS
\noindent\textbf{Guidance on abstract writing:} An abstract is a summary of a report in a single paragraph up to a maximum of 250 words. An abstract should be self-contained, and it should not refer to sections, figures, tables, equations, or references. An abstract typically consists of sentences describing the following four parts: (1) introduction (background and purpose of the project), (2) methods, (3) results and analysis, and (4) conclusions. The distribution of these four parts of the abstract should reflect the relative proportion of these parts in the report itself. An abstract starts with a few sentences describing the project's general field, comprehensive background and context, the main purpose of the project; and the problem statement. A few sentences describe the methods, experiments, and implementation of the project. A few sentences describe the main results achieved and their significance. The final part of the abstract describes the conclusions and the implications of the results to the relevant field.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%s
~\\[1cm]
\noindent % Provide your key words
\textbf{Keywords:} a maximum of five keywords/keyphrase separated by commas

\vfill
\noindent
\textbf{Report's total word count: Following the abstract, the word count must be stated.} We expect at least 10,000 words in length and at most 15,000 words (starting from Chapter 1 and finishing at the end of the conclusions chapter, excluding references, appendices, abstract, text in figures, tables, listings, and captions), about 40 - 50 pages. \newline
\newline
\noindent
\textbf{Program code should be uploaded to gitlab, and the gitlab link should be included alongside the word count, following the abstract.} \newline
\newline
You must submit your dissertation report (preferred in a PDF file) via the “Turnitin assignment” in Blackboard Learn by the deadline. If a student has resits from the taught modules, the dissertation deadline will be extended for 3 weeks from the original dissertation deadline.

